---
title: "ecom2"
output: github_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Insalling libraries
library(readr)
library(rfm)
library(skimr)
library(ggplot2)
library(gganimate)  
library(janitor)
library(plyr)
library(lubridate)
library(dplyr)
library(knitr)
library(tableHTML)
library(treemap)



#Importing the dataset
```

##Importing the dataset

```{r importing data}

retailsales <- read.csv("eCommerce Dataset - data.csv")
```

##Getting to know the data


```{r pressure}
glimpse(retailsales)

head(retailsales)
```

## Top 5 rows of the data

```{r top5}


head(retailsales,5)
```


#Running summarises of the dataset 

```{r dup}
#Removing possible duplicates

retailsales2 <- unique(retailsales)

#Noticed null values in the Customer ID column during exploration, removing them

retailsales2 <- na.omit(retailsales2, select = c("CustomerID"))
```

###Noticed null values in the Customer ID column during exploration, removing them

```{r nullvalues}

retailsales2 <- na.omit(retailsales2, select = c("CustomerID"))
```


#Converting the date column from character format to a date time format

```{r con}
str(retailsales2$InvoiceDate) #Confirming the 'InvoiceDate' column has changed to date time format
glimpse(retailsales2$InvoiceDate)
retailsales2$InvoiceDate <- as.Date(retailsales2$InvoiceDate)
```



```{r con2}



#The cancelled order contain an 'InvoiceNo' that begins with a 'C', we won't be needing those for this analysis as our focus are our most valuable customers

retailsales2 <- retailsales2[!grepl("^C", retailsales2$InvoiceNo), ]
head(retailsales2$InvoiceNo)
```


###The cancelled order contain an 'InvoiceNo' that begins with a 'C', we won't be needing those for this analysis as our focus are our most valuable customers

```{r can}


#Dropping the 'StockCode,' and 'Description' column as they won't be necessary for the analysis

retailsales2 <- retailsales2 %>%  
  select(-c( StockCode,Description))

#The cancelled order contain an 'InvoiceNo' that begins with a 'C', we won't be needing those for this analysis as our focus are our most valuable customers

retailsales2 <- retailsales2[!grepl("^C", retailsales2$InvoiceNo), ]
head(retailsales2$InvoiceNo)
```



##Exploratory data analysis 

###Calculating the revenue and including a revenue column

```{r exp2}

#retailsales2$revenue <- paste0("?", formatC(retailsales2$revenue, format = "f", digits = 2, big.mark = ","))
#glimpse(retailsales2$revenue)

retailsales2$revenue <- retailsales2$Quantity * retailsales2$UnitPrice
head(retailsales2$revenue)

```


#Extracting month from the 'InovoiceDate'column


```{r exp}
library(tidyr)
retailsales3<-retailsales2 %>% 
              
                      mutate(InvoiceDate = as_datetime(InvoiceDate), month_col=month(InvoiceDate,label = TRUE,abbr=FALSE), sort_mnt  =month(InvoiceDate)) %>% 
 drop_na()


ggplot(retailsales3, aes(x = month_col, y = revenue)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Month", y = "Revenue", title = "Revenue by Month")+
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE))+ coord_flip()  # Formatting y-axis labels
  


```
